Production-maintenance scheduling in complex machinery

### 2024-03-26 Paper.tex
Mostly everything fixed

\begin{table}[!htb]
    %\caption{Global caption}
      \centering
      %\hspace{-2cm}
          \resizebox{0.75\textwidth}{!}{
\begin{tabular}{ |p{1.5cm}||p{5.3cm}|p{4cm}|  }
     \hline
     Parameter & Parameter Meaning & Parameter Range\\
     \hline
     \hline
    $\cmss{C}^k$   &  Cost of maintaining component $k$   & $\mathbb{R}^{+}$\\
    $\cmss{D}^k$  & Duration of component $k$'s maintenance & $\mathbb{N}$\\
    $\cmss{E}_t$   & Demand at period $t$ & $\mathbb{R}^{+}$\\
    $\mathcal{K}$   &  Components to be maintained & \\
    \cmss{M} & Big constant to dominate constraint & $\mathbb{R}^{+}$\\
    $\mathcal{N}$ & Set of machines & $\mathbb{N}$\\
    $\cmss{Q}^k$   &  Maximum permissible production & $\mathbb{R}^{+}$\\
    $\cmss{R}^k$   &  Maximum condition of component $k$  & $\mathbb{R}^{+}$\\
    $\mathcal{T}$   &  Set of periods   & $\mathbb{N}$\\
    $\mathcal{Z}$  & Set of maintenance implications & $\mathcal{K}^n \times \mathcal{K}^n$\\

@@

\begin{table}[!htb]
      \centering
          \resizebox{0.75\textwidth}{!}{

\begin{tabular}{ |p{1.25cm}||p{6.5cm}|p{2.5cm}|  }
     \hline
     Variable & Variable Meaning & Variable Type\\
     \hline
     \hline
    $x^k_{n,t}$   &  Maintenance of component $k$ of machine $n$ at period $t$   & Binary\\
    $y_{n,t}$   &  Production of machine $n$ at period $t$ & Continuous\\
    $r^k_{n,t}$   &  Condition of component $k$ of machine $n$ at period $t$  & Continuous\\
    \hline
    \end{tabular}
}
        \caption{Description of the variables used in the model}
        \label{tab:abstract_variable_description}    
\end{table}

@@

\todo[inline]{KB: you should be consistent about the capitalisation of the section titles (i.e. same level headings should have similar capitalisation). JD@KB:Done.}
\todo[inline]{KB: I would add some introductory text here.}

@@

@@

\todo[inline]{KB: put this right after the first sentence of the section, since this is background. The paper's contribution would better go next.} An iterative refinement heuristic that would be applicable to this problem can be found in~\cite{An_Optimization_Model_for_Power_Transformer_Maintenance}, whose idea is limiting the number of maintenance possibilities and expanding them with every iteration.
As this work did not yield a large improvement, we omit it from this paper.

\subsubsection{The production-fixing heuristic} This heuristic tries to take advantage of the impact of the production variable on the model.
Given a fixed production vector, the idea is to perform maintenance at the last possible moment, where if any maintenance action were to be delayed by one time period, the solution would be infeasible.
This maintenance strategy is referred to as just-in-time maintenance.
For a fixed production vector, Constraints~\eqref{con:production_limit} will fix the condition of the components, sans the maintenance. 
Heuristically, the fixed production vector is chosen given the Farkas' duals or the actual duals of the current iteration. 
Assuming a normal distribution with mean and standard deviation provided by these duals, the production will benefit more the more unlikely high its dual is. %Heuristically, the decision of which values the variables should be fixed to is being done with pattern-search (also known as the Hooke-Jeeves method)~\cite{Direct_Search_Solution_of_Numerical_and_Statistical_Problems}, where each variable is independently increased and decreased, and improving moves are saved. The algorithm iterates over all the variables until either a time limit or a local optimum is reached.

However, even if we select the best possible production vector, this heuristic is not optimal.
This is due to the interaction between components when it comes to their degradation, but also to the maintenance implication constraints (\eqref{con:maintenance_implications}).
See the following example:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Below follows the production-fixing algorithm used in this work. ??? WORK IN PROGRESS ???

@@

Onto the main procedure, $\cmss{PF-heuristic}$, we start by calling $\cmss{getProduction}$ to obtain the production vector, using the dual values given by the current iteration of the master problem. 
Iterating first over the components and then over the time periods (otherwise the impact that the components have on each others' condition would be evaluated incorrectly), we compute the condition of the current component for the current time period, as every variable of Constraint~\ref{con:component_degradation} is fixed, sans maintenance. 
If the resulting condition is incompatible with the production (see Constraint~\ref{con:production_limit}), then maintenance is scheduled. 
This means setting production to $0$, the condition to its optimal value, and the maintenance variables to $1$, for the duration of component $k$'s maintenance (lines $12-15$). 
Line $11$ ensures that a component does not start maintenance that it would not be able to finish.

@@

A lot more work can go into this heuristic. 
The choice of the production vector in Algorithm~\ref{algo:getProduction} should be more substantiated, and the results mentioned in the beginning of the section regarding maintenance anticipation should also provide better results.

\todo[inline]{KB: this assumption is important, so I would move it closer to the beginning of the section. 
And may be mention whether the heuristic would still produce any meaningful results for the non-concave case.}
This heuristic also assumes the concavity of function $f$, as otherwise not setting $r^k_t$ to its upper bound (which we do in line $9$ of Algorithm~\ref{algo:PF}) might yield a better solution. 
However, we were unable to create a realistic example where this would not be the case, in the context of production-maintenance scheduling.

@@

\todo[inline]{KB: please double check that this is indeed what you meant: I rephrased the sentence}
The varying combinations of time period numbers, complexity and numbers of machines and identical machines yield $10\cdot 3\cdot 2\cdot 3 = 180$ different instances.

@@

\todo[inline]{KB: don't you already have different complexities in the previous tables?}
\begin{table}[!htb]
  \caption{Comparing effect of machine complexity}

@@

As expected, the decomposition approaches appear advantageous, in comparison to the compact model, when increasing the number of identical machines. On the other hand, having more machines increases the number of pricing problems, and longer time-horizons increase their difficulty, so the compact formulation seems better suited for these instances.

@@

     The Dantzig-Wolfe reformulation can still be improved, as the heuristic used to generate new columns does not fully utilize the duals provided by the master problem. Doing multiple iterations of the cheap pricing problem while adding benders-like optimality cuts, could be a better strategy for faster convergence. ??????

>>>>

\todo[inline]{JD: I made the tables bigger. What do you think?}

\begin{table}[!htb]
    %\caption{Global caption}
      \centering
      %\hspace{-2cm}
          \resizebox{0.9\textwidth}{!}{
\begin{tabular}{ |p{1.5cm}||p{6cm}|p{3cm}|  }
     \hline
     Parameter & Parameter Meaning & Parameter Range\\
     \hline
    $\cmss{C}^k$   &  Cost of maintaining component $k$   & $\mathbb{R}^{+}$\\
    $\cmss{D}^k$  & Duration of component $k$'s maintenance & $\mathbb{N}$\\
    $\cmss{E}_t$   & Demand at period $t$ & $\mathbb{R}^{+}$\\
    $\mathcal{K}$   &  Components to be maintained & \\
    \cmss{M} & Big constant to dominate constraint & $\mathbb{R}^{+}$\\
    $\mathcal{N}$ & Set of machines & $\mathbb{N}$\\
    $\cmss{Q}^k$   &  Maximum permissible production & $\mathbb{R}^{+}$\\
    $\cmss{R}^k$   &  Maximum condition of component $k$  & $\mathbb{R}^{+}$\\
    $\mathcal{T}$   &  Set of periods   & $\mathbb{N}$\\
    $\mathcal{Z}$  & Set of maintenance implications & $\mathcal{K}^n \times \mathcal{K}^n$\\

@@

\vspace*{-3em}

\begin{table}[!htb]
      \centering
          \resizebox{1\textwidth}{!}{

\begin{tabular}{ |p{1.25cm}||p{8cm}|p{2.5cm}|  }
     \hline
     Variable & Variable Meaning & Variable Type\\
     \hline
    $x^k_{n,t}$   &  Maintenance of component $k$ of machine $n$ at period $t$   & Binary\\
    $y_{n,t}$   &  Production of machine $n$ at period $t$ & Continuous\\
    $r^k_{n,t}$   &  Condition of component $k$ of machine $n$ at period $t$  & Continuous\\
    \hline
    \end{tabular}
}
        \caption{Description of the variables used in the model}
        \label{tab:abstract_variable_description}    
\end{table}

@@

\todo[inline]{KB: you should be consistent about the capitalisation of the section titles (i.e. same level headings should have similar capitalisation). JD@KB:Done.}
\todo[inline]{KB: I would add some introductory text here. JD@KB: Done.}

Implementing Branch-and-Price requires a lot of effort.
Fortunately SCIP~\cite{scip9.0}, the solver used in our work, is equipped with a Branch-and-Price framework.
Nevertheless, there remains some problem-specific details which need to be implemented, described in this Section.

@@

\todo[inline]{KB: put this right after the first sentence of the section, since this is background. The paper's contribution would better go next. JD@KB: Done.} An iterative refinement heuristic that would be applicable to this problem can be found in a previous work of ours~\cite{An_Optimization_Model_for_Power_Transformer_Maintenance}, whose idea is limiting the number of maintenance possibilities and expanding them with every iteration.
As this heuristic did not yield a large improvement, we omit it from this paper.

@@

\label{subsubsec:PF}
\subsubsection{The production-fixing heuristic} This heuristic tries to take advantage of the impact of the production variable on the model.
Given a fixed production vector, the idea is to perform maintenance at the last possible moment, where if any maintenance action were to be delayed by one time period, the solution would be infeasible.
This maintenance strategy is referred to as just-in-time maintenance.
For a fixed production vector, Constraints~\eqref{con:production_limit} will fix the condition of the components, sans the maintenance. 
Heuristically, the fixed production vector is chosen given the Farkas' duals or the actual duals of the current iteration. 
Assuming a normal distribution with mean and standard deviation provided by these duals, the production will benefit more the more unlikely high its dual is. %Heuristically, the decision of which values the variables should be fixed to is being done with pattern-search (also known as the Hooke-Jeeves method)~\cite{Direct_Search_Solution_of_Numerical_and_Statistical_Problems}, where each variable is independently increased and decreased, and improving moves are saved. The algorithm iterates over all the variables until either a time limit or a local optimum is reached.

\todo[inline]{KB: this assumption is important, so I would move it closer to the beginning of the section. 
And maybe mention whether the heuristic would still produce any meaningful results for the non-concave case. JD@KB: Done} 
This heuristic assumes the concavity of function $f$ for a fixed $y$.
However, we were unable to create a realistic example where this would not be the case, in the context of production-maintenance scheduling.
It seems sensible to assume that if a component's condition affects another's degradation, then the worse the condition of the former, the higher the impact on the latter.
In the event of a nonconcave relationship, the heuristic will incorrectly mark more production vectors as unattainable, and will also provide worse solution the less concave the degradation.
In this case the heuristic still works, but its benefit will be limited.

However, even if function $f$ is concave for a fixed $y$, and we select the best possible production vector, this heuristic is not optimal.
This is due to the interaction between components when it comes to their degradation, but also to the maintenance implication constraints (\eqref{con:maintenance_implications}).
See the following example:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Below follows the production-fixing algorithm used in this work.

@@

Onto the main procedure, $\cmss{PF-heuristic}$, we start by calling $\cmss{getProduction}$ to obtain the production vector, using the dual values given by the current iteration of the master problem. 
Iterating first over the components and then over the time periods (otherwise the impact that the components have on each others' condition would be evaluated incorrectly), we compute the condition of the current component for the current time period, as every variable of Constraint~\ref{con:component_degradation} is fixed, sans maintenance.
(And here is the assumption of concavity of $f$ for a fixed $y$, as otherwise setting the component's condition to a value lower than its upper bound might be better.) 
If the resulting condition is incompatible with the production (see Constraint~\ref{con:production_limit}), then maintenance is scheduled. 
This means setting production to $0$, the condition to its optimal value, and the maintenance variables to $1$, for the duration of component $k$'s maintenance (lines $12-15$). 
Line $11$ ensures that a component does not start maintenance that it would not be able to finish.

@@

% more assertive?
The choice of the production vector in Algorithm~\ref{algo:getProduction} can be more substantiated, and the results mentioned in the beginning of the section regarding maintenance anticipation should also provide better results, meaning that this heuristic can be improved upon.

@@

\todo[inline]{KB: please double check that this is indeed what you meant: I rephrased the sentence. JD@KB: Done. Rephrased a bit as well.}
The varying combinations of time periods, complexity and machine groups yield $10\cdot 3\cdot 2\cdot 3 = 180$ different instances.

@@

\todo[inline]{KB: don't you already have different complexities in the previous tables? JD@KB: Yeah, I still need to think how I want to present the results...}
\begin{table}[!htb]
  \caption{Comparing effect of machine complexity}

@@

As expected, the decomposition approaches appear advantageous in comparison to the compact model when increasing the number of identical machines. On the other hand, having more machines increases the number of pricing problems, and longer time-horizons increase their difficulty, so the compact formulation seems better suited for these instances.

@@

    The heuristic proved to be a good complement to exact pricing.
    Besides the comments at the end of the heuristic's description, we are considering taking better advantage of how fast the heuristic is.
    Our idea is doing multiple iterations of the heuristic with different production vectors, while adding benders-like optimality and feasibility cuts, which should provide significantly better columns.
